Anony\emph{mice}d shareable data: Using \emph{mice} to create and analyze multiply imputed synthetic data sets

### 2021-11-03 manuscript/blind_rev/Manuscript.Rmd
Blind revisions.

---
title: "Anony*mice*d shareable data: Using *mice* to create and analyze multiply imputed synthetic data sets"
author:
  - name: Thom Benjamin Volker
    affil: 1,*, \dagger
    orcid: 0000-0002-2408-7820
  - name: Gerko Vink
    affil: 1, \dagger
    orcid: 0000-0001-9767-1924
affiliation:
  - num: 1
    address: |
      Utrecht University - 
      Department of Methodology and Statistics. 
      Padualaan 14. 3584CH Utrecht, the Netherlands
# firstnote to eighthnote
firstnote: |
  These authors contributed equally to this work.
correspondence: |
  t.b.volker@uu.nl.
journal: psych
type: article
status: submit
bibliography: synth.bib
appendix: appendix.tex
abstract: |
  Synthetic data sets simultaneously allow for the dissemination of research data
  while protection the privacy and confidentiality of respondents. Generating 
  and analyzing synthetic data sets is straightforward, yet a synthetic data analysis 
  pipeline is seldom adopted by applied researchers. We outline a simple procedure 
  for generating and analyzing synthetic data sets with the multiple imputation
  software `mice` in `R`. We demonstrate using simulations that the analysis 
  results obtained on synthetic data yield unbiased and valid inferences, and 
  leads to synthetic records that cannot be distinguished from the true data records. 
  The ease of use when synthesizing data with `mice`, together with the validity of 
  inferences obtained through this procedure opens up a wealth of possibilities for 
  data dissemination and further research of initially private data. 
keywords: |
  mice; multiple imputation; synthetic data; statistical disclosure control; privacy.
acknowledgement: |
  We are grateful to Mirthe Hendriks and Stijn van den Broek for replicating the 
  simulation study on an independent data set. Additionally, we thank Hanne Oberman, 
  two anonymous reviewers and the editor for their helpful and insightful comments.
authorcontributions: |
  The authors contributed equally to this work.
conflictsofinterest: |
  The authors declare no conflict of interest. 
sampleavailability: |
  A full simulation archive is available from https://github.com/amices/Federated_imputation/tree/master/manuscript.
output: rticles::mdpi_article
---

>>>>

---
title: "Anony*mice*d shareable data: Using *mice* to create and analyze multiply imputed synthetic data sets"
firstnote: |
  These authors contributed equally to this work.
journal: psych
type: article
status: submit
bibliography: synth.bib
appendix: appendix.tex
abstract: |
  Synthetic data sets simultaneously allow for the dissemination of research data
  while protection the privacy and confidentiality of respondents. Generating 
  and analyzing synthetic data sets is straightforward, yet a synthetic data analysis 
  pipeline is seldom adopted by applied researchers. We outline a simple procedure 
  for generating and analyzing synthetic data sets with the multiple imputation
  software `mice` in `R`. We demonstrate using simulations that the analysis 
  results obtained on synthetic data yield unbiased and valid inferences, and 
  leads to synthetic records that cannot be distinguished from the true data records. 
  The ease of use when synthesizing data with `mice`, together with the validity of 
  inferences obtained through this procedure opens up a wealth of possibilities for 
  data dissemination and further research of initially private data. 
keywords: |
  mice; multiple imputation; synthetic data; statistical disclosure control; privacy.
acknowledgement: |
  We are grateful to Mirthe Hendriks and Stijn van den Broek for replicating the 
  simulation study on an independent data set. Additionally, we thank Hanne Oberman, 
  two anonymous reviewers and the editor for their helpful and insightful comments.
authorcontributions: |
  The authors contributed equally to this work.
conflictsofinterest: |
  The authors declare no conflict of interest. 
sampleavailability: |
  A full simulation archive is available from the zip-enclosed .Rmd file.
output: rticles::mdpi_article
---

### 2021-11-03 manuscript/blind_rev/Manuscript.tex
Blind revisions.

% Authors, for the paper (add full first names)
\Author{Thom Benjamin Volker$^{1,*,
\dagger}$\href{https://orcid.org/0000-0002-2408-7820}{\orcidicon}, Gerko
Vink$^{1,
\dagger}$\href{https://orcid.org/0000-0001-9767-1924}{\orcidicon}}

% Authors, for metadata in PDF
\AuthorNames{Thom Benjamin Volker, Gerko Vink}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Utrecht University - Department of Methodology and
Statistics. Padualaan 14. 3584CH Utrecht, the Netherlands; \\
}
% Contact information of the corresponding author
\corres{Correspondence: \href{mailto:t.b.volker@uu.nl}{\nolinkurl{t.b.volker@uu.nl}}.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\sampleavailability{A full simulation archive is available from
\url{https://github.com/amices/Federated_imputation/tree/master/manuscript}.}

>>>>

% Authors, for the paper (add full first names)
\Author{}

% Authors, for metadata in PDF
\AuthorNames{}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
}
% Contact information of the corresponding author
\corres{Correspondence: }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\sampleavailability{A full simulation archive is available from the
zip-enclosed .Rmd file.}
